Supplementary Materials for: Empowering the use of community driven preprints in ecology and evolution

### 2024-03-23 supp/supp.qmd
Adding citation results

# Load packages
#install.packages("pacman")
pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, ggthemes, mapproj, DemografixeR, countrycode)

@@

# Now we can use the first name and the country (that's important) to get an idea of the persons gender. 
genders <- genderize(data2$submitting_author_firstname, country_id = data2$submitting_author_country_code, simplify = FALSE)

@@

>>>>

# Load packages
#install.packages("pacman")
pacman::p_load(tidyverse, here, patchwork, readxl, MASS, googlesheets4, janitor, maps, forcats,RColorBrewer, flextable, ggrepel, ggimage, gt, performance, ggthemes, mapproj, DemografixeR, countrycode, see)

@@

# Now we can use the first name and the country (that's important) to get an idea of the persons gender. 
genders <- genderize(data2$submitting_author_firstname, country_id = data2$submitting_author_country_code, simplify = FALSE)
write.csv(genders, here("data", "gender_dat.csv"))

@@

## Preprint citations versus published article citations

```{r, fig-citations}

# First, we need to extract the published articles
pubs <- data2  %>% filter(!is.na(time_between_preprint_and_pub_days))

# We will need to re-oragnise the dataframe in long format for analysis.
data_long_cites <- pubs  %>% dplyr::select(preprint_id, preprint_doi, publication_date, time_between_preprint_and_pub_days, number_of_citations_preprint, number_of_citations_article)  %>% pivot_longer(cols = c(number_of_citations_preprint, number_of_citations_article), names_to = "type", values_to = "citations")  %>% mutate(type = ifelse(type == "number_of_citations_preprint", "Preprint", "Published Article"))

# Now we can plot the data
ggplot(data_long_cites, aes(x = type, y = sqrt(citations))) +
  geom_violinhalf(aes(fill = type), flip = 1) + geom_jitter(shape=16, position=position_jitter(0.01), alpha = 0.2) + geom_line(aes(group = preprint_id), alpha = 0.2, colour = "black") +
  labs(x = "Paper Status", y = "Number of citations (sqrt transformed)") +
  theme_bw() + theme(legend.position = "none")
```
